---
output: pdf_document
---
Homework 0: Eclectic Eagle Scouts

### Implementation

This function takes as input a list or non-logical vector that can be flattened, coerced, or rounded into an integer vector of absolute values. Upon execution, it prints this vector of positive integers, with multiples of 3 replaced with 'Fizz', multiples of 5 by 'Buzz', and multiples of 15 by 'FizzBuzz'. Internally, the vector of positive integers is assigned to a vector, out. Multiples of 3, 5, and 15 are replaced with text via modulus-based logical-vector subsetting, in the process coercing out to a character vector. Finally, the vector is concatenated and printed, one element per line. If, however, the input is logical or cannot be coerced to a numeric, an error is thrown.

```{r, echo=T}
FizzBuzz = function(n) {
  if(!anyNA(suppressWarnings(as.numeric(unlist(n)))) & !any(is.logical(n))) {
    out = n = abs(round(as.numeric(unlist(n))))
    out[n %% 3)==0] = 'Fizz'
    out[n %% 5)==0] = 'Buzz'
    out[n %% 15)==0] = 'FizzBuzz'
    out[n==0] = 0
    cat(out, sep='\n')
  } else {
    warning('Input cannot be coerced or rounded to positive integers.')
  }  
}
```



### Output

```{r}
FizzBuzz(1:100)
FizzBuzz('asdf')
FizzBuzz(list(5.6, '6.7', -7.8, 9:10))
```
